Efficient Handling of String-Number Conversion

### 2020-04-04 final-version/evaluation.tex
update experiments to use release version of all tools

We compare {\tool} (\texttt{1e715b7dab})\footnote{\url{https://github.com/guluchen/z3/tree/1e715b7dab}} with other state-of-the-art string solvers, namely, CVC4~(version 1.7)~\cite{cvc4Tool}, Z3~(version 4.8.7)~\cite{z3}, and \textsf{Z3Str3}~(version 4.8.7)~\cite{zheng2013z3}. For these tools, the versions we used are the latest release versions. \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occur in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support many of the string functions in our benchmarks, especially string-number conversion.

@@

	\changed{All experiments were executed on a machine with 4-core CPU, 16 GiB RAM, and MacOS 10.15.4.} The timeout was set to 10s for each test.
We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results. Occasionally, two of them report inconsistent  answers (one SAT and one UNSAT). To decide which solver is right, we developed a validator. It takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtain a modified test, and re-evaluates the modified test by multiple solvers. If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results. Otherwise, we manually simplify and inspect the test until we get a conclusive result.

@@

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 21377& 19899& 16331&  3037 \\
							& UNSAT    &  3860&  3848&  3831&  3816 \\
							& UNKNOWN  &     0&     0&     0&     7 \\
							& TIMEOUT  &   184&  1674&  5259& 16872 \\
							& ERROR    &     0&     0&     0&  1675 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline
%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
%							& UNSAT    &   286&   214&   100&   111 \\
%							& UNKNOWN  &     0&     0&     0&   345 \\
%							& TIMEOUT  &   188&   335&   487&    89 \\
%							& ERROR    &     0&     0&     0&    20 \\
%							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   877&   865&   881&   661 \\
							& UNSAT    &  1785&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    0&    16&     0&    90 \\
							& ERROR    &     4&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   515&   704&   267&   505 \\
							& UNSAT    &   301&   245&   188&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   249&   116&   610&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   822&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     0&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     8&     5&    2 \\
							& UNSAT    &  1032&  1025&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     3&    12&    18&    58 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 22792& 21487& 17496&  4213\\
							& UNSAT    &  7800&  7721&  7634&  7519\\
							& UNKNOWN  &     0&     0&     0&   140\\
							& TIMEOUT  &  436&  1824&  5902& 17422 \\
							& ERROR    &     4&     0&     0&  1710\\
							& INCORRECT&     0&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1721&  1898&   239 \\ 
								& UNSAT    & 16394& 15726& 16115& 15288 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &    32&  1480&   914&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     0&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &  1922&   579&   914&   206 \\ 
								& UNSAT    &   724&   667&   724&   642 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &     0&  1400&  1008&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
								& UNSAT    &     0&     0&     0&     0 \\
								& UNKNOWN  &     0&     9&     0&     0 \\
								& TIMEOUT  &     0&     8&     4&    10 \\
								& ERROR    &     0&     0&     0&     6 \\
								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  4443&  2303&  2828&   449 \\ 
								& UNSAT    & 17118& 16393& 16839& 15930 \\
								& UNKNOWN  &     0&     9&     0&   668 \\
								& TIMEOUT  &    32&  2888&  1926&  4057 \\
								& ERROR    &     0&     0&     0&   379 \\
								& INCORRECT&     0&     0&     0&   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
}
\end{table}

>>>>

We compare {\tool} (\texttt{1e715b7dab})\footnote{\url{https://github.com/guluchen/z3/tree/1e715b7dab}} with other state-of-the-art string solvers, namely, CVC4~(version 1.7)~\cite{cvc4Tool}, Z3~(version 4.8.7)~\cite{z3}, and \textsf{Z3Str3}~(version 4.8.7)~\cite{zheng2013z3}. For these tools, the versions we used are the latest release version. \changed{Observe that CVC4 and Z3 are  DPLL(T)-based string solvers.}
We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occur in most of our benchmarks. We also do not compare with ABC~\cite{aydin2018parameterized} (a model counter for string constraints), Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{abdulla2019chain}, because they do not support many of the string functions in our benchmarks, especially string-number conversion.

@@

	\changed{All experiments were executed on a machine with 4-core CPU and 16 GiB RAM.} The timeout was set to 10s for each test.
We use the results from {\tool}, CVC4, and Z3 as the reference answer for the validation of the correctness of the results. Occasionally, two of them report inconsistent  answers (one SAT and one UNSAT). To decide which solver is right, we developed a validator. It takes the model $I$ returned from the solver who reported SAT, assigns $I(x)$ to all variables $x$ in the test to obtain a modified test, and re-evaluates the modified test by multiple solvers. If the results from all solvers are consistent, we mark the test SAT or UNSAT according to the results. Otherwise, we manually simplify and inspect the test until we get a conclusive result.

@@

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on Basic String Constraint benchmarks.}
\scalebox{0.85}{
\begin{tabular}{|l r | r r r r |}
\hline
\multicolumn{2}{|c}{}                  & {\tool} & CVC4  &Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{PyEx}		& SAT      & 21377& 20350& 18492&  3037 \\
							& UNSAT    &  3860&  3841&  3847&  3816 \\
							& UNKNOWN  &     0&     0&     0&     7 \\
							& TIMEOUT  &   184&  1230&  3082& 16872 \\
							& ERROR    &     0&     0&     0&  1675 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline
%\multirow{6}{*}{APLAS}		& SAT      &   126&    51&    13&    35 \\
%							& UNSAT    &   286&   214&   100&   111 \\
%							& UNKNOWN  &     0&     0&     0&   345 \\
%							& TIMEOUT  &   188&   335&   487&    89 \\
%							& ERROR    &     0&     0&     0&    20 \\
%							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{LeetCode}	& SAT      &   877&   874&   881&   661 \\
							& UNSAT    &  1785&  1785&  1785&  1780 \\
							& UNKNOWN  &     0&     0&     0&   122 \\
							& TIMEOUT  &    0&    7&     0&    90 \\
							& ERROR    &     4&     0&     0&    13 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{StringFuzz}	& SAT      &   515&   615&   338&   505 \\
							& UNSAT    &   301&   255&   198&   192 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &   249&   195&   529&   364 \\
							& ERROR    &     0&     0&     0&     0 \\
							& INCORRECT&     0&     0&     0&     0 \\\hline
\multirow{6}{*}{cvc4\textsubscript{pred}} & SAT &    13&    11&    12&     8 \\
							& UNSAT    &   822&   818&   808&   774 \\
							& UNKNOWN  &     0&     0&     0&     4 \\
							& TIMEOUT  &     0&     6&    15&    38 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&     0 \\ \hline
\multirow{6}{*}{cvc4\textsubscript{term}} & SAT &    10&     9&     7&    2 \\
							& UNSAT    &  1032&  1026&  1022&   957 \\
							& UNKNOWN  &     0&     0&     0&     3 \\
							& TIMEOUT  &     3&    10&    16&    58 \\
							& ERROR    &     0&     0&     0&     11 \\
							& INCORRECT&     0&     0&     0&    14 \\ \hline \hline
\multirow{6}{*}{Total} 		& SAT      & 22792& 21859& 19730&  4213\\
							& UNSAT    &  7800&  7725&  7550&  7519\\
							& UNKNOWN  &     0&     0&     0&   140\\
							& TIMEOUT  &  436&  1448&  3642& 17422 \\
							& ERROR    &     4&     0&     0&  1710\\
							& INCORRECT&     0&     0&     0&    28 \\\hline
\end{tabular}}
\label{table:base_benchmark}}
\end{table}

\begin{table}[h]
\changed{
\centering
\caption{Results of {\tool}, CVC4, Z3, and Z3Str3 on String-Number Conversion benchmark.}
\scalebox{0.8}{
\begin{tabular}{|l r | r r r r|}
\hline
\multicolumn{2}{|c}{}          			   & {\tool} &  CVC4 &    Z3 & Z3Str3 \\ \hline
\multirow{6}{*}{Leetcode}		& SAT      &  2501&  1659 &  1993&   239 \\ 
								& UNSAT    & 16394& 15604& 16124& 15288 \\
								& UNKNOWN  &     0&     0&     0&   623 \\
								& TIMEOUT  &    32&  1664&   810&  2337 \\
								& ERROR    &     0&     0&     0&   332 \\
								& INCORRECT&     0&     0&     0&   108 \\ \hline 
\multirow{6}{*}{PythonLib}		& SAT      &  1922&   560&   1839&   206 \\ 
								& UNSAT    &   724&   666&   724&   642 \\
								& UNKNOWN  &     0&     0&     0&    45 \\
								& TIMEOUT  &     0&  1420&  83&  1710 \\
								& ERROR    &     0&     0&     0&    41 \\
								& INCORRECT&     0&     0&     0&     2 \\ \hline
\multirow{6}{*}{JavaScript}		& SAT      &    20&     3&    16&     4 \\ 
								& UNSAT                &     0&     0&     0&     0 \\
								& UNKNOWN         &     0&     9&     0&     0 \\
								& TIMEOUT            &     0&     8&     4&    10 \\
								& ERROR                &     0&     0&     0&     6 \\
								& INCORRECT&     0&     0&     0&     0 \\ \hline \hline
\multirow{6}{*}{Total}			& SAT      &  4443&  2222     &  3848    &   449 \\ 
								& UNSAT            & 17118 & 16270     & 16848   & 15930 \\
								& UNKNOWN      &     0   &     9        &     0       &   668 \\
								& TIMEOUT         &    32  &  3092     &  897     &  4057 \\
								& ERROR             &     0   &     0        &     0        &   379 \\
								& INCORRECT     &     0   &     0        &     0         &   110 \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
}
\end{table}
